Age-related changes in plant growth and traits

### 2015-05-19 results_best.Rmd
file "results_accessory_shorter" includes a synthesis of most accessory costs thoughts

source("scripts/summary_dataframes.R")

plot_yvar_vs_xvar <- function(data, yvar = "y", xvar = "x", ...) {
  Y <- data[[yvar]]
  X <- data[[xvar]]
  plot(Y ~ X, data=data,  cex.axis=.8, las=1, pch=16, ...)
}

@@

words.bottom.right.logxy <- function (x) {
output <- data.frame(select(glance(x), r.squared, p.value))
output <- round(output,4)
text(10^((0.75*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.12*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("r squared = ",output[1]),adj=0,cex=.9)
text(10^((0.75*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.07*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("p-value = ",output[2]),adj=0,cex=.9)
text(10^((0.99*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.02*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),summary(mod)[1],cex=.7,adj=1)
}
```

@@

##RV curves (by proportion max H)
- In a sense, by using proportion max H, these figures are showing the proportion of total growth the plant undergoes before starting reproduction
- The plot across all species of reproductive investment vs. Prop H is much less tight than reproductive investment vs. total weight, but within a species not as obviously different  
- The plot that includes all species shows that *once* a given species has ramped up reproduction, the log-log plot of reproductive investment vs final weight is nearly linear across all species; in other words, to first order, all species allocate the same amount to reproduction relative to their weight.  
- This is presumably the basic allometric scaling relationship discussed by others and wondering if slope I get is same as theirs    
- However, it is important to note that species early in their reproductive trajectory do not follow this pattern  
```{r, echo=FALSE,message=FALSE}
plot((ReproInv)~(PropH), SummaryInd, log="y",col=col.spp[as.factor(species)],pch=16,xlim=c(4e-03,1))
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

@@

plot(ReproInv~height, SummaryInd, log="xy",col=col.spp[as.factor(species)],pch=16)
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

yvar <- "ReproInv"
xvar <- "PropH"

@@

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, 
                    main=spp, log="y", xlab=xvar, ylab=yvar)
}
```

@@

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,
                    main=spp, xlab=xvar, ylab=yvar)
}
```

@@

##Across species patterns of note
###Size versus proportional propagule investment
- Species that are bigger (by weight) invest a lower proportion of their reproduction in propagules  
   1.  This is another way of showing that larger species get less of a return on their investment in reproduction. They have higher accessory costs. 
   - There is also an increase in propagule investment with age
```{r, echo=FALSE, message=FALSE}
mod <- lm(log(FinalWeight) ~ (log(PerPropagule))+age,data=subset(SummaryInd,PerPropagule>0))
summary(mod)
plot(PerPropagule ~FinalWeight, data=subset(SummaryInd,RA>0&PerPropagule>0),log="xy", col=col.spp[as.factor(species)],pch=16)
legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.top.right.logxy(mod)
text(10^((0.70*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.85*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),"includes age effect",adj=0) 
```

@@

results
```
#getting counts out of Konrad's reproduction data - this code now also appears in "summary_dataframe.R", where it belongs in the end

```{r, echo=FALSE, message=FALSE}
tmp <- BAER_Investment
FD <- as.data.frame(tmp$FD)
BAER_count <- FD %>%
  group_by(Individual, what) %>%
  summarise_each(funs(sum), count, weight)
BAER_count <- subset(BAER_count, count!=0)
BAER_count$species <- "BAER"

tmp <- BOLE_Investment
FD <- as.data.frame(tmp$FD)
BOLE_count <- FD %>%
  group_by(Individual, what) %>%
  summarise_each(funs(sum), count, weight)
BOLE_count <- subset(BOLE_count, count!=0)
BOLE_count$species <- "BOLE"

tmp <- COER_Investment
FD <- as.data.frame(tmp$FD)
COER_count <- FD %>%
  group_by(Individual, what) %>%
  summarise_each(funs(sum), count, weight)
COER_count <- subset(COER_count, count!=0)
COER_count$species <- "COER"

tmp <- EPMI_Investment
FD <- as.data.frame(tmp$FD)
EPMI_count <- FD %>%
  group_by(Individual, what) %>%
  summarise_each(funs(sum), count, weight)
EPMI_count <- subset(EPMI_count, count!=0)
EPMI_count$species <- "EPMI"

tmp <- GRBU_Investment
FD <- as.data.frame(tmp$FD)
GRBU_count <- FD %>%
  group_by(Individual, what) %>%
  summarise_each(funs(sum), count, weight)
GRBU_count <- subset(GRBU_count, count!=0)
GRBU_count$species <- "GRBU"

tmp <- GRSP_Investment
FD <- as.data.frame(tmp$FD)
GRSP_count <- FD %>%
  group_by(Individual, what) %>%
  summarise_each(funs(sum), count, weight)
GRSP_count <- subset(GRSP_count, count!=0)
GRSP_count$species <- "GRSP"

tmp <- HATE_Investment
FD <- as.data.frame(tmp$FD)
HATE_count <- FD %>%
  group_by(Individual, what) %>%
  summarise_each(funs(sum), count, weight)
HATE_count <- subset(HATE_count, count!=0)
HATE_count$species <- "HATE"

tmp <- HEPU_Investment
FD <- as.data.frame(tmp$FD)
HEPU_count <- FD %>%
  group_by(Individual, what) %>%
  summarise_each(funs(sum), count, weight)
HEPU_count <- subset(HEPU_count, count!=0)
HEPU_count$species <- "HEPU"

tmp <- LEES_Investment
FD <- as.data.frame(tmp$FD)
LEES_count <- FD %>%
  group_by(Individual, what) %>%
  summarise_each(funs(sum), count, weight)
LEES_count <- subset(LEES_count, count!=0)
LEES_count$species <- "LEES"

tmp <- PELA_Investment
FD <- as.data.frame(tmp$FD)
PELA_count <- FD %>%
  group_by(Individual, what) %>%
  summarise_each(funs(sum), count, weight)
PELA_count <- subset(PELA_count, count!=0)
PELA_count$species <- "PELA"

tmp <- PEPU_Investment
FD <- as.data.frame(tmp$FD)
PEPU_count <- FD %>%
  group_by(Individual, what) %>%
  summarise_each(funs(sum), count, weight)
PEPU_count <- subset(PEPU_count, count!=0)
PEPU_count$species <- "PEPU"

tmp <- PHPH_Investment
FD <- as.data.frame(tmp$FD)
PHPH_count <- FD %>%
  group_by(Individual, what) %>%
  summarise_each(funs(sum), count, weight)
PHPH_count <- subset(PHPH_count, count!=0)
PHPH_count$species <- "PHPH"

tmp <- PILI_Investment
FD <- as.data.frame(tmp$FD)
PILI_count <- FD %>%
  group_by(Individual, what) %>%
  summarise_each(funs(sum), count, weight)
PILI_count <- subset(PILI_count, count!=0)
PILI_count$species <- "PILI"

tmp <- PUTU_Investment
FD <- as.data.frame(tmp$FD)
PUTU_count <- FD %>%
  group_by(Individual, what) %>%
  summarise_each(funs(sum), count, weight)
PUTU_count <- subset(PUTU_count, count!=0)
PUTU_count$species <- "PUTU"

accessory_count <- rbind(BAER_count,BOLE_count,COER_count,EPMI_count,GRBU_count,GRSP_count,HATE_count,HEPU_count,LEES_count,PELA_count,PEPU_count,PHPH_count,PILI_count,PUTU_count)
```

TO DO
- seed set with age - this is probably what explains a lot of changes in proportional tissue alotment. 
-Big question is if seed set changes with plant size or age

>>>>

source("scripts/summary_dataframes.R")
plot_yvar_vs_xvar <- function(data, yvar = "y", xvar = "x", ...) {
  Y <- data[[yvar]]
  X <- data[[xvar]]
  plot(Y ~ X, data=data,  cex.axis=.8, las=1, pch=16, ...)
}

plot_yvar2_vs_xvar2 <- function(data, yvar2 = "y", xvar2 = "x", ...) {
  Y <- data[[yvar2]]
  X <- data[[xvar2]]
  plot(Y ~ X, data=data,  cex.axis=.8, las=1, pch=16, ...)
}

@@

words.bottom.right.logxy <- function (x) {
output <- data.frame(select(glance(x), r.squared, p.value))
output <- round(output,4)
text(10^((0.75*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.12*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("r squared = ",output[1]),adj=0,cex=.9)
text(10^((0.75*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.07*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("p-value = ",output[2]),adj=0,cex=.9)
text(10^((0.99*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.02*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),summary(mod)[1],cex=.7,adj=1)
}

words.bottom.right.logx <- function (x) {
  output <- data.frame(select(glance(x), r.squared, p.value))
  output <- round(output,4)
  text(10^((0.75*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.12*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("r squared = ",output[1]),adj=0,cex=.9)
  text(10^((0.75*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.07*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("p-value = ",output[2]),adj=0,cex=.9)
  text(10^((0.99*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.02*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),summary(mod)[1],cex=.7,adj=1)
}
```

@@

##RV curves (by proportion max H)
- In a sense, by using proportion max H, these figures are showing the proportion of total growth the plant undergoes before starting reproduction
- The plot across all species of reproductive investment vs. Prop H is much less tight than reproductive investment vs. total weight, but within a species not as obviously different  
- The plot that includes all species shows that *once* a given species has ramped up reproduction, the log-log plot of reproductive investment vs final weight is nearly linear across all species; in other words, to first order, all species allocate the same amount to reproduction relative to their weight.  
- This is presumably the basic allometric scaling relationship discussed by others and wondering if slope I get is same as theirs    
- However, it is important to note that species early in their reproductive trajectory do not follow this pattern

```{r, echo=FALSE,message=FALSE, fig.width=12, fig.height=6, out.width=792, out.height=576}
yvar <- "RA"
xvar <- "PropH"

yvar2 <- "RA"
xvar2 <- "FinalWeight"

data <- SummaryInd
data <- split(data, data$species)

for(spp in names(data)) {
  par(mfrow=c(1,2), cex=1, omi=c(.1,0.3,.5,0.2), mai=c(1.2,1,.5,0.2))  
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, 
                    main=spp, xlab=xvar, ylab=yvar)
  plot_yvar2_vs_xvar2(data[[spp]], yvar2, xvar2, 
                    main=spp, log="x", xlab=xvar2, ylab="")

}

plot.new()
```

```{r, echo=FALSE,message=FALSE, fig.width=12, fig.height=6, out.width=792, out.height=576}
yvar <- "ReproInv"
xvar <- "PropH"

yvar2 <- "ReproInv"
xvar2 <- "FinalWeight"

data <- SummaryInd
data <- split(data, data$species)

for(spp in names(data)) {
  par(mfrow=c(1,2), cex=1, omi=c(.1,0.3,.5,0.2), mai=c(1.2,1,.5,0.2))  
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, 
                    main=spp, ,log="y", xlab=xvar, ylab=yvar)
  plot_yvar2_vs_xvar2(data[[spp]], yvar2, xvar2, 
                    main=spp, log="xy", xlab=xvar2, ylab="")

}

par(mfrow=c(1,1), pin=c(5,7),mar=c(5,4,4,2)+.1,omi=c(.1,.1,.1,.1))
```

```{r, echo=FALSE,message=FALSE, fig.width=7, fig.height=7, out.width=792, out.height=576}
plot((ReproInv)~(PropH), SummaryInd, log="y",col=col.spp[as.factor(species)],pch=16,xlim=c(4e-03,1),xlab=xvar)
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

@@

plot(ReproInv~height, SummaryInd, log="xy",col=col.spp[as.factor(species)],pch=16)
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
```

* Reproductive investment vs. PropH
```{r, echo=FALSE,message=FALSE, fig.width=7, fig.height=7, out.width=792, out.height=576}
yvar <- "ReproInv"
xvar <- "PropH"

@@

@@

@@

##Across species patterns of note
###Size versus proportional propagule investment
- Species that are bigger (by weight) invest a lower proportion of their reproduction in propagules  
   1.  This is another way of showing that larger species get less of a return on their investment in reproduction. They have higher accessory costs. 
   - There is also an increase in propagule investment with age
```{r, echo=FALSE,message=FALSE, fig.width=14, fig.height=7, out.width=792, out.height=576}
mod <- lm(log(FinalWeight) ~ (log(PerPropagule))+age,data=subset(SummaryInd,PerPropagule>0))
summary(mod)
plot(PerPropagule ~FinalWeight, data=subset(SummaryInd,RA>0&PerPropagule>0),log="xy", col=col.spp[as.factor(species)],pch=16)
legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.top.right.logxy(mod)
text(10^((0.70*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.85*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),"includes age effect",adj=0) 
```

@@
